<span style="color:red;">*ANTs*</span><br> <small>_power tools for neuroimaging_</small>

### 2014-10-30 ants2015build.Rmd
ENH:  Adding to title slide.
BUG:  Wrong filename.

## Regional importance comparison

@@

<div align="center"><img height="500" src="./evaluation/figures/antsvfreesurfer_importance.png" frameborder="0"></img></div>

@@

# *ANTs* and the perils of circularity

>>>>

## Regional importance <br>comparison

@@

<div align="center"><img height="500" src="./evaluation/figures/antsvfreesurfer_Importance.png" frameborder="0"></img></div>

@@

# *ANTs* and the perils of circularity<br><br>[<small>"*Logical circularity in voxel-based analysis: normalization strategy may induce statistical bias*"</small>](http://www.ncbi.nlm.nih.gov/pubmed/23151955)
